\documentclass{article}

\usepackage{fancyhdr}
\usepackage{extramarks}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{tikz}
\usepackage[plain]{algorithm}
\usepackage{algpseudocode}
\usepackage{hyperref}

\usetikzlibrary{automata,positioning}

%
% Basic Document Settings
%

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1}

\pagestyle{fancy}
\lhead{\hmwkAuthorName}
\chead{\hmwkClass\ : \hmwkTitle}
\rhead{\hmwkClassInstructor}
\cfoot{\thepage}

\renewcommand\headrulewidth{0.4pt}
\renewcommand\footrulewidth{0.4pt}

\setlength\parindent{0pt}
%
% Homework Details
%   - Title
%   - Due date
%   - Class
%   - Section/Time
%   - Instructor
%   - Author
%

\newcommand{\hmwkTitle}{Report Week 2}
\newcommand{\hmwkDueDate}{January 27, 2020}
\newcommand{\hmwkClass}{URMP}
\newcommand{\hmwkClassInstructor}{Panayot Vassilevski}
\newcommand{\hmwkAuthorName}{\textbf{Austen Nelson}}

%
% Title Page
%

\title{
    \vspace{2in}
    \textmd{\textbf{\hmwkClass:\ \hmwkTitle}}\\
    \normalsize\vspace{0.1in}\small{\hmwkDueDate}\\
    \vspace{0.1in}\large{\textit{\hmwkClassInstructor}}
    \vspace{3in}
}

\author{\hmwkAuthorName}
\date{}

\begin{document}

\maketitle
\pagebreak

\section{Progress}
This week I made decent progress on cleaning and organizing the data I collected. I spent some time annotating my ingredient phrases with
tags so I could put my data through a conditional random field to parse out the extra information and separate a phase into quantity,
measurement, and name. The tool I used is CRF++. This tool doesn't have any API and only deals with external data files but I integrated the
installed program into my rust data-flow. The accuracy isn't prefect but it is working well enough to begin analysis. My dataset has over 40,000
recipes with around 15,000 unique ingredients. With this information it was pretty trivial to create the bipartite graph between recipes and
ingredients. I did some very basic exploration like looking at the most commonly used ingredients.

\section{Plans}
The next step will be to create the other data structures that I have planned and begin doing analysis on the data. I'm still doing research
on the analysis that I am going to do and am meeting with my advisor on Thursday the 30th. I also plan on writing some other scrapers and spiders
for recipes other than allrecipes. Even though the allrecipes database is large, it seems to be lower quality and geared towards writing
recipes around products that companies pay the site to promote. It would be interesting to see if analysis differs between platforms.

\end{document}
